Appendix of Bauer et al. (2023) Dike experiment

### 2023-02-22 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.

@@

The community-weighted means (CWM) of the seed mixtures used for the field experiment: specific leaf area (SLA), seed mass and canopy height. The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target types hay meadows and dry calcareous grasslands. The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].

@@

### Acknowledgment

This figure has been supported by the TRY initiative on plant traits (<http://www.try-db.org>). The TRY initiative and database is hosted, developed and maintained by J. Kattge and G. Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany). TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.

@@

```{r tab.id = "specieslist", tab.cap = ""}
read_csv(
  here("outputs", "tables", "table_a4_specieslist.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  mutate(name = str_replace_all(name, "_", " ")) %>%
  rename(Name = name, "Presence [# plots]" = sum) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(j = 2, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
  autofit()
```

>>>>

All sown seed mixtures can be found on GitHub in the folder \`outputs/tables/ table_a2_seed_mixtures.csv\`. There it is indicated which species are combined and the ratio in the specific seed mixture.

@@

@@

The community-weighted means (CWM) of the seed mixtures used for the dike experiment: specific leaf area (SLA), seed mass and canopy height. The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target habitat types hay meadows and calcareous grasslands. The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].

#### Acknowledgment

This figure was supported by the TRY initiative on plant traits (<http://www.try-db.org>). The TRY initiative and database is hosted, developed and maintained by J. Kattge and G. Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany). TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig. \clearpage \newpage

@@

```{r tab.id = "specieslist", tab.cap = ""}
read_csv(
  here("outputs", "tables", "table_a5_specieslist.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  mutate(name = str_replace_all(name, "_", " ")) %>%
  rename(
    Name = name,
    Seeded = seeded,
    "Target species" = target,
    "Presence [# plots]" = sum
    ) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(j = 4, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
  autofit()
```
